Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping

### 2018-01-30 stp/paper_aaai/main.tex
Minor tweaks

Most approaches to solve the \relonto{} problem are based on 
heuristic rules and alignment of constraints specified within relational 
schemata and ontologies.
\citeasnoun{Pinkel:rodi} and~\citeasnoun{Spanos:semweb} give
a very comprehensive overview and comparison of existing mapping generation 
tools based on this approach.
As examples, there are BootOX~\cite{Jimenez:Bootox}, MIRROR~\cite{Luciano:Mirror} and  ontop~\cite{Fagin:Clio}.
Briefly, these tools first apply a default direct mapping specified by the W3C.
Then, the default ontology is enriched by using explicit and implicit schema constraints.
Finally, ontology alignment techniques are applied to match the default ontology to the target ontology.
The main advantage of these systems is that they are fully automatic\forijcai{ the ability to run in a fully automatic setting}.
Our approach is complementary to them and at its current stage is semi-automatic.
However, CP offers a convenient framework to incorporate integrity constraints specified \forijcai{either} within relational or ontological schema as additional constraints to govern the search for the solution.
\forijcai{This opens an interesting direction for further research.}

A major issue with fully automatic systems is that constraints may be 
inconsistent or absent completely, e.g., data from Web services or tables on 
the Web.
To overcome this issue,
\citeasnoun{Limaye:Annotating} design a ML system to annotate web tables with 
entities for cell values, semantic labels for attributes and relationships for 
binary combinations of attributes.
As in our approach, they decompose the process of mapping into two main stages: semantic labeling and finding relationships between matched semantic labels.
\citeasnoun{Limaye:Annotating} enrich their data sources by using YAGO \cite{suchanek2007yago}.
\citeasnoun{Mulwad:Semantic} extend this approach by leveraging information 
from Wikitology Knowledge Base (KB).
\citeasnoun{Venetis:Recovering} develop a scalable approach to recover the 
semantics of Web tables by incorporating data from the isA database KB.
\citeasnoun{Ritze:matching}, on the other hand, use DBPedia as their KB.
%extract additional data from knowledge bases to assign a semantic label to an attribute.
Hence, these approaches are limited to domains well represented in those knowledge bases.
Also, they are not able to find the relation between attributes in the table if there is no direct connection between the attributes.
Our approach, on the other hand, allows a model to be trained on any data and can infer complex semantic paths which might exist between attributes.
However, it could be further bootstrapped by leveraging external knowledge bases.
This is especially beneficial when the system does not have sufficient training data.

>>>>

Most approaches to solve the \relonto{} problem are based on 
heuristic rules and alignment of constraints specified within relational 
schemata and ontologies.
\citeasnoun{Pinkel:rodi} and~\citeasnoun{Spanos:semweb} give
a comprehensive overview and comparison of existing mapping generation 
tools based on this approach.
As examples, there are BootOX~\cite{Jimenez:Bootox}, MIRROR~\cite{Luciano:Mirror} and  ontop~\cite{Fagin:Clio}.
Briefly, these tools first apply a default direct mapping specified by the W3C.
Then, the default ontology is enriched by using explicit and implicit schema constraints.
Finally, ontology alignment techniques are applied to match the default ontology to the target ontology.
The main advantage of these systems is that they are fully automatic\forijcai{ the ability to run in a fully automatic setting}.
Our approach is complementary to them and at its current stage is semi-automatic.
However, CP offers a convenient framework to incorporate integrity constraints specified \forijcai{either} within relational or ontological schema as additional constraints to govern the search for the solution.
\forijcai{This opens an interesting direction for further research.}

A major issue with fully automatic systems is that constraints may be 
inconsistent or absent completely, e.g., data from Web services or tables on 
the Web.
To overcome this issue,
\citeasnoun{Limaye:Annotating} design a ML system to annotate web tables with 
entities for cell values, semantic labels for attributes and relationships for 
binary combinations of attributes.
As in our approach, they decompose the process of mapping into two main stages: semantic labeling and finding relationships between matched semantic labels.
\citeasnoun{Limaye:Annotating} enrich their data sources by using YAGO Knowledge Base (KB)\cite{suchanek2007yago}.
\citeasnoun{Mulwad:Semantic} extend this approach by leveraging information 
from Wikitology KB.
\citeasnoun{Venetis:Recovering} develop a scalable approach to recover the 
semantics of Web tables by incorporating data from the isA database KB.
\citeasnoun{Ritze:matching}, on the other hand, use DBPedia as their KB.
%extract additional data from knowledge bases to assign a semantic label to an attribute.
Hence, these approaches are limited to domains well represented in those knowledge bases.
Also, they are not able to find the relation between attributes in the table if there is no direct connection between the attributes.
Our approach, on the other hand, allows a model to be trained on any data and can infer complex semantic paths which might exist between attributes.
However, it could be further bootstrapped by leveraging external knowledge bases.
This is especially beneficial when the system does not have sufficient training data.
